FTLR proof cases

### 2018-06-29 fully-abstract-comp/ftlr-proof-cases.tex
Reply to Dominique comment.

  The property for $\lrv$ follows from the other properties, by definition, from Lemma~\ref{lem:n-equality-props}, non-expansiveness of regions \dominique{Is $\xi$ non-expansive/contractive/?}
  TODO

>>>>

  The property for $\lrv$ follows from the other properties, by definition, from Lemma~\ref{lem:n-equality-props}, non-expansiveness of regions \dominique{Is $\xi$ non-expansive/contractive/?}
  \lau{I believe it is at-least non-expansive and monotone as it is a morphism in the category of preordered c.o.f.e.'s.
    Do you also ``need'' it to be contractive?}
  TODO
